An Open Platform for Managing Short Programming Exercises

### 2013-06-24 paper/paper.tex
some minor phrasing improvements

CloudCoder executes Java, Python, and Ruby code relatively securely using
a Java Security Manager.
(CloudCoder uses Jython\cite{jython} and JRuby\cite{jruby}
to execute Python and Ruby submissions, allowing us to take advantage of
the Java Security Manager for those languages.)
CloudCoder's execution of C/C++ code is somewhat less secure, although 
in the near future
we hope to take advantage of a better sandboxing mechanism,
possibly based on the work of
David Malan for Harvard's online CS50 course\cite{Malan:2013:CSS:2445196.2445242}.
However, because thus far the only users of
CloudCoder have been instructors and students,
the weak sandboxing has not been a significant concern.

@@

To date, each institution that has adopted CloudCoder in production has
provided Linux servers that we configured for them.  This has made
adoption very easy, but is not a model that is likely to scale well
to larger numbers of institutions.  We recently received a grant
of credits for Amazon Web Services\cite{aws} from Amazon,
which we plan to use to directly host CloudCoder for interested
institutions.  We are also investigating easier ways for
users to self-host, such as enabling CloudCoder to run on application
hosting services such as Google App Engine\cite{gae}.
%  We have asked Amazon for Amazon Web Services credits to
%provide CloudCoder ``in the cloud'' to adopting institutions, and we
%hope to add support for Google App Engine this summer.  Ease of
%adoption is critical for CloudCoder.

>>>>

CloudCoder executes Java, Python, and Ruby code relatively securely using
a Java Security Manager.
(CloudCoder uses Jython\cite{jython} and JRuby\cite{jruby}
to execute Python and Ruby submissions, allowing us to take advantage of
the Java Security Manager for those languages.)
CloudCoder's execution of C/C++ code is somewhat less secure, although 
in the near future
we hope to take advantage of a better sandboxing mechanism,
possibly based on the work of
David Malan for Harvard's online CS50 course\cite{Malan:2013:CSS:2445196.2445242}.
However, because thus far the only users of
CloudCoder have been instructors and students,
the weak sandboxing of C/C++ submissions has not been a significant concern.

@@

To date, each institution that has adopted CloudCoder in production has
provided Linux servers that we configured for them.  This has made
adoption very easy, but is not a model that is likely to scale well
to larger numbers of institutions.  We recently received a grant
of credits for Amazon Web Services\cite{aws} from Amazon,
which we plan to use to directly host CloudCoder for interested
institutions.  We are also investigating easier ways for
users to self-host. One possibility is enabling CloudCoder to run on application
hosting services such as Google App Engine\cite{gae}.
%  We have asked Amazon for Amazon Web Services credits to
%provide CloudCoder ``in the cloud'' to adopting institutions, and we
%hope to add support for Google App Engine this summer.  Ease of
%adoption is critical for CloudCoder.
